### 2022-11-22 ms.rmd
Added new model that also deals with trait category

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################
phylo_cor <- vcv(tree_p0.7, cor = TRUE)
A <- vcv(tree_p0.7, cor = FALSE) # For bayes

@@

@@

# Intercept only model. 
rerun = TRUE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}

@@

## Contrasts
posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
f_acute  <- posteriors_1.2[,"b_Intercept"] 
f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]

# Orchard plot
p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + 
  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") + 
  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
annotate("text", x = 1, y = 2.10, 
         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
annotate("text", x = 1.01, y = 4.60, 
         label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)

>>>>

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################

@@

# Check and prune tree
tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good

# Create the phylo correlation matrix
phylo_cor <- vcv(tree_lnrr, cor = TRUE)
        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix

@@

# Intercept only model. 
rerun = FALSE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}

@@

## Contrasts
posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
f_acute  <- posteriors_1.2[,"b_Intercept"] 
pmcmc(f_acute)
f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]

# R2
fix <- var(predict(model1.2_bayes)[,"Estimate"])
r2_ml(model1.2)

# Orchard plot
results1.2 <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)

p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + 
  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") + 
  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
annotate("text", x = 1, y = 2.10, 
         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
annotate("text", x = 1.01, y = 4.60, 
         label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)

 if(rerun){
  # More realistic model with 
  model1.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + habitat + type:habitat + trait_category:habitat:type + trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

   model1.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)

  # Save model1.2
  saveRDS(model1.3, file = "./output/models/lnRRQ10_1.3")
  saveRDS(model1.3_bayes, file = "./output/models/lnRRQ10_1.3_bayes")

  } else{
  model1.3 <- readRDS("./output/models/lnRRQ10_1.3")
  model1.3_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes")
}
